---
title: "Bioeconomic_Model_Final_Draft"
author: "Ashley Cooper"
date: "2024-03-14"
output:
    html_document:
      theme: flatly
      code_folding: hide

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(nloptr)
library(knitr)
library(kableExtra)
library(dplyr)
library(ggplot2)
library(cowplot)
library(scales)
library(patchwork)
library(gridExtra)
```

*int stock* = initial biomass (MT)

$X_t$ = fish stock (MT) at time *t*

$h_t$ = quota, or legal fishing effort (MT)

$discount (\delta)$ = .05

$p$ = price of landed fish (per MT)

$c$ = cost of fishing (per MT)

$\alpha$ = cost of enforcement

$e_{t}$ = enforcement effort at time *t*

$\gamma$ = enforcement effectiveness

$K$ = carrying capacity

$r$ = intrinsic population growth rate

**Stock Equation**

$$
X_{t+1} = X_{t} + r*X_{t} - \frac{r *(X_{t})^2}{K} -(h_t)
$$

**Benefits Function**

$$
\pi_t = p*(h_t) - c * \frac{(h_t)^2}{X_t}
$$

### Parameters

```{r}
### Time parameters
T = 20 #time horizon for backward induction; t is the equivalent of i, and is used for while-loops
discount <- 0.05
delta <- 1/(1+discount)


### Biological parameters
K <- 2265128
r <- 0.2
int_stock <- 883400 # initial stock biomass (MT)
grid_start <- K/1000000 # guess for xgrid in optimal policy/value functions

### Economic parameters
p <- 2397
c <- 1678

### Enforcement parameters
enfVec <- seq(0, 1, .1) # Enforcement vector from 0 to 1, with 0 being no enforcement and 1 being full enforcement
enfDet <- c(0, .04, .25, .38, .47, .54, .59, .64, .68, .72, .75)/3 # Taken from McDonald et al. code
fine <- p * 3.5


### Iteration parameters
sizex = 100 # size of the state grid; setting equal to Chris C's example
xgrid <- seq(grid_start, K, length.out = sizex)

tol_ht = .01 # tolerance value for fishing effort optimization
tol_e = .01 # tolerance value for enforcement effort optimization
```

### Dynamic Optimal Harvest w/ Value Function Iteration (VFI)

#### Value Function Iteration


```{r, results=FALSE}
### Stock function
stock_growth_fun <- function(h, X)
{
  Xnext = X + (r * X) - (r * X^2)/K - h
  if (X < 0) Xnext = 0
  return (Xnext)
}

### Profits function
profit_legal <- function(h, X)
{
  benefit = p*h - c * (h^2)/X
}

### Payoff function to get long-term benefits. V = Value
payoff <- function(X, h, V)
{
  Xnext = stock_growth_fun(h, X)
  Vnext = spline(x = xgrid, y = V, xout = Xnext)
  neg_out = -(profit_legal(h,X) + delta * Vnext$y) # sum of current profit + discounted future value of fish
  return(neg_out) # negative because of optimization
}

DFall = data.frame()
Vnext = vector()
V = seq(0, 0, length.out = sizex) # Setting V = 0

### Payoff function

optimzation_1 <- for(t in T:1)
{
  print(t)
  
  for(i in 1:length(xgrid))
  {
    X = xgrid[i]
    guess = 10
    low = 0 # lower bound on harvest
    high = X + (r * X) - (r * X^2)/K # upper bound; harvest cannot exceed stock (growth?). could also try high = X
    Thing = optim(par = guess, fn = payoff, lower = low, upper = high, X = X, V = V, method = 'L-BFGS-B')
    hstar = Thing$par #optimal harvest, or quota
    Vstar = -Thing$value #optimal value
    Vnext[i] = Vstar
    
    ### now use dataframe to store information
    DFnow = data.frame(time = t, X = X, hstar = hstar, Vstar = Vstar)
    DFall = bind_rows(DFall, DFnow)
  } # end for loop
  
  V = Vnext # tells the model to iterate
}
```


#### Forward Simulation


```{r}
### Forward simulation, choosing time 1 (convergence) as the time

DFopt <- DFall %>% 
  filter(time==1)


hpol = DFopt$hstar #optimal harvest policy
xpol = DFopt$X
xsim = vector()
hsim = vector()

xsim[1] = int_stock  # Elected to start with int_stock because this is the starting biomass of yellowfin tuna at the time of model creation
Tsim = seq(1, 20)

for(tt in Tsim)
{
  Thing = spline(x = xpol, y = hpol, xout = xsim[tt])
  hsim[tt] = Thing$y
  if(tt < max(Tsim))
  {
   xsim[tt+1] = stock_growth_fun(h = hsim[tt], X = xsim[tt]) 
  }
}

DFsimulation <- data.frame(time = Tsim, xsim = xsim, hsim = hsim) %>% 
  mutate(enfE = rep("Optimal", 20)) %>% 
  mutate(stock = round(xsim)) %>% 
  mutate(legal = round(spline(x = DFopt$X, y = DFopt$hstar, xout = xsim)$y)) %>% 
  mutate(legal = ifelse(legal > hsim, round(hsim), legal)) %>% 
  mutate(illegal = round(hsim - legal)) %>% 
  mutate(illegal = ifelse(illegal < 0, 0, illegal)) %>% 
  mutate(total = legal + illegal)
```


### Introduce Illegal Fishing


#### Starting Functions


```{r}
### Adapted from profitOptimEnf (Optimization to determine vector of optimal fishing effort and optimal enforcement effort based on B/BMSY)

### Fine function
fine_fun <- function(ht, h)
  {
  if (ht > h)
    {expected_fine = spline(enfVec, enfDet, xout = enforcement)$y * (ht - h) * fine}
      
    else 
      {expected_fine = 0}
  
    return(expected_fine)
}

### Social profit function
profit_social_fun <- function(ht, h, X)
  {
  if (X == 0)
    {profit = 0}
  
  else
    {profit = p * ht - c * ht^2/X - fine_fun(ht, h)}
  
  return(profit)
}

### Function to find the approximate hstar value in DFopt for a given stock level X
approx_hstar_fun <- function(X)
  {
  if (any(X == 0)) 
    {approx_hstar = 0}
  
  else
    {approx_hstar = spline(x = DFopt$X, y = DFopt$hstar, xout = X)$y}
  
  return(approx_hstar)
}

payoff_illegal <- function(ht, X, V2)
{
  Xnext = stock_growth_fun(ht, X)
  Vnext = spline(x = xgrid, y = V2, xout = Xnext)
  # neg_out = -(profit_social_fun(ht, h = approx_hstar_fun(X), X) + delta * Vnext$y)
  neg_out = -(profit_social_fun(ht, h = approx_hstar_fun(X), X))
  return(neg_out)
}
```


### Enforcment = 0

```{r, results=FALSE}
### VFI

#### Payoff function

enforcement <- 0

DFall_illegal_0e = data.frame()
Vnext_illegal_0e = vector
V2 = seq(0, 0, length.out = sizex)

actual_optimization <- for(t in T:1)
{
  print(t)
  
  for(i in 1:length(xgrid))
  {
    X = xgrid[i]
    guess = 10
    
    Fishes = optim(par = guess,
                   fn = payoff_illegal,
                   lower = 0,
                   upper = X,
                   X = X,
                   V2 = V2,
                   method = 'L-BFGS-B')
    
    hactual = Fishes$par # Actual harvest
    value = -Fishes$value # Value of the actual harvest
    Vnext[i] = value
    
    ### DF to store information to store information
    DFnow_illegal_0e = data.frame(time = t, X = X, hactual = hactual, value = value)
    DFall_illegal_0e = bind_rows(DFall_illegal_0e, DFnow_illegal_0e)
  }

  V2 = Vnext # tells the model to iterate  

}
```


```{r}
#### Forward Simulation

DF_opt_illegal_0e <- DFall_illegal_0e %>% 
  filter(time == 1)

xsim2 = vector()
hsim2 = vector()

xsim2[1] = int_stock
Tsim = seq(1, 20)

for(t in Tsim)
{
  Fishes2 = spline(x = DF_opt_illegal_0e$X, y = DF_opt_illegal_0e$hactual, xout = xsim2[t])
  hsim2[t] = Fishes2$y
  if(t < max(Tsim))
  {
   xsim2[t+1] = stock_growth_fun(h = hsim2[t], X = xsim2[t]) 
  }
}

DFsimulation_0e <- data.frame(time = Tsim, xsim = xsim2, hsim = hsim2) %>% 
  mutate(enfE = rep("0", 20)) %>% 
  mutate(stock = round(xsim)) %>% 
  mutate(legal = round(spline(x = DFopt$X, y = DFopt$hstar, xout = xsim)$y)) %>% 
  mutate(legal = ifelse(legal > hsim, round(hsim), legal)) %>% 
  mutate(illegal = round(hsim - legal)) %>% 
  mutate(illegal = ifelse(illegal < 0, 0, illegal)) %>% 
  mutate(total = legal + illegal)
```


### Enforcement = 0.25

```{r, results=FALSE}
### VFI

#### Payoff function
enforcement <- 0.25

DFall_illegal_0.25e = data.frame()
Vnext_illegal_0.25e = vector
V2 = seq(0, 0, length.out = sizex)

actual_optimization <- for(t in T:1)
{
  print(t)
  
  for(i in 1:length(xgrid))
  {
    X = xgrid[i]
    guess = 10
    
    Fishes = optim(par = guess,
                   fn = payoff_illegal,
                   lower = 0,
                   upper = X,
                   X = X,
                   V2 = V2,
                   method = 'L-BFGS-B')
    
    hactual = Fishes$par # Actual harvest
    value = -Fishes$value # Value of the actual harvest
    Vnext[i] = value
    
    ### DF to store information to store information
    DFnow_illegal_0.25e = data.frame(time = t, X = X, hactual = hactual, value = value)
    DFall_illegal_0.25e = bind_rows(DFall_illegal_0.25e, DFnow_illegal_0.25e)
  }

  V2 = Vnext # tells the model to iterate  

}


#### Forward Simulation

DF_opt_illegal_0.25e <- DFall_illegal_0.25e %>% 
  filter(time == 1)

xsim2 = vector()
hsim2 = vector()

xsim2[1] = int_stock
Tsim = seq(1, 20)

for(t in Tsim)
{
  Fishes2 = spline(x = DF_opt_illegal_0.25e$X, y = DF_opt_illegal_0.25e$hactual, xout = xsim2[t])
  hsim2[t] = Fishes2$y
  if(t < max(Tsim))
  {
   xsim2[t+1] = stock_growth_fun(h = hsim2[t], X = xsim2[t]) 
  }
}

DFsimulation_0.25e <- data.frame(time = Tsim, xsim = xsim2, hsim = hsim2) %>% 
  mutate(enfE = rep("0.25", 20)) %>% 
  mutate(stock = round(xsim)) %>% 
  mutate(legal = round(spline(x = DFopt$X, y = DFopt$hstar, xout = xsim)$y)) %>% 
  mutate(legal = ifelse(legal > hsim, round(hsim), legal)) %>% 
  mutate(illegal = round(hsim - legal)) %>% 
  mutate(illegal = ifelse(illegal < 0, 0, illegal)) %>% 
  mutate(total = legal + illegal)
```


### Enforcement = 0.5

```{r, results=FALSE}
### VFI

#### Payoff function
enforcement <- 0.5

DFall_illegal_0.5e = data.frame()
Vnext_illegal_0.5e = vector
V2 = seq(0, 0, length.out = sizex)

actual_optimization <- for(t in T:1)
{
  print(t)
  
  for(i in 1:length(xgrid))
  {
    X = xgrid[i]
    guess = 10
    
    Fishes = optim(par = guess,
                   fn = payoff_illegal,
                   lower = 0,
                   upper = X,
                   X = X,
                   V2 = V2,
                   method = 'L-BFGS-B')
    
    hactual = Fishes$par # Actual harvest
    value = -Fishes$value # Value of the actual harvest
    Vnext[i] = value
    
    ### DF to store information to store information
    DFnow_illegal_0.5e = data.frame(time = t, X = X, hactual = hactual, value = value)
    DFall_illegal_0.5e = bind_rows(DFall_illegal_0.5e, DFnow_illegal_0.5e)
  }

  V2 = Vnext # tells the model to iterate  

}


#### Forward Simulation

DF_opt_illegal_0.5e <- DFall_illegal_0.5e %>% 
  filter(time == 1)

xsim2 = vector()
hsim2 = vector()

xsim2[1] = int_stock
Tsim = seq(1, 20)

for(t in Tsim)
{
  Fishes2 = spline(x = DF_opt_illegal_0.5e$X, y = DF_opt_illegal_0.5e$hactual, xout = xsim2[t])
  hsim2[t] = Fishes2$y
  if(t < max(Tsim))
  {
   xsim2[t+1] = stock_growth_fun(h = hsim2[t], X = xsim2[t]) 
  }
}

DFsimulation_0.5e <- data.frame(time = Tsim, xsim = xsim2, hsim = hsim2) %>%
  mutate(enfE = rep("0.5", 20)) %>% 
  mutate(stock = round(xsim)) %>% 
  mutate(legal = round(spline(x = DFopt$X, y = DFopt$hstar, xout = xsim)$y)) %>% 
  mutate(legal = ifelse(legal > hsim, round(hsim), legal)) %>% 
  mutate(legal = ifelse(legal < 0, 0, legal)) %>% 
  mutate(illegal = round(hsim - legal)) %>% 
  mutate(illegal = ifelse(illegal > hsim, round(hsim), illegal)) %>% 
  mutate(illegal = ifelse(illegal < 0, 0, illegal)) %>% 
  mutate(total = legal + illegal)
```


### Enforcement = 0.75

```{r, results=FALSE}
### VFI

#### Payoff function
enforcement <- 0.75

DFall_illegal_0.75e = data.frame()
Vnext_illegal_0.75e = vector
V2 = seq(0, 0, length.out = sizex)

actual_optimization <- for(t in T:1)
{
  print(t)
  
  for(i in 1:length(xgrid))
  {
    X = xgrid[i]
    guess = 10
    
    Fishes = optim(par = guess,
                   fn = payoff_illegal,
                   lower = 0,
                   upper = X,
                   X = X,
                   V2 = V2,
                   method = 'L-BFGS-B')
    
    hactual = Fishes$par # Actual harvest
    value = -Fishes$value # Value of the actual harvest
    Vnext[i] = value
    
    ### DF to store information to store information
    DFnow_illegal_0.75e = data.frame(time = t, X = X, hactual = hactual, value = value)
    DFall_illegal_0.75e = bind_rows(DFall_illegal_0.75e, DFnow_illegal_0.75e)
  }

  V2 = Vnext # tells the model to iterate  

}


#### Forward Simulation

DF_opt_illegal_0.75e <- DFall_illegal_0.75e %>% 
  filter(time == 1)

xsim2 = vector()
hsim2 = vector()

xsim2[1] = int_stock
Tsim = seq(1, 20)

for(t in Tsim)
{
  Fishes2 = spline(x = DF_opt_illegal_0.75e$X, y = DF_opt_illegal_0.75e$hactual, xout = xsim2[t])
  hsim2[t] = Fishes2$y
  if(t < max(Tsim))
  {
   xsim2[t+1] = stock_growth_fun(h = hsim2[t], X = xsim2[t]) 
  }
}

DFsimulation_0.75e <- data.frame(time = Tsim, xsim = xsim2, hsim = hsim2) %>% 
  mutate(enfE = rep("0.75", 20)) %>% 
  mutate(stock = round(xsim)) %>% 
  mutate(legal = round(spline(x = DFopt$X, y = DFopt$hstar, xout = xsim)$y)) %>% 
  mutate(legal = ifelse(legal > hsim, round(hsim), legal)) %>% 
  mutate(illegal = round(hsim - legal)) %>% 
  mutate(illegal = ifelse(illegal < 0, 0, illegal)) %>% 
  mutate(total = legal + illegal)
```

### Enforcement = 1


```{r, results=FALSE}
### VFI

#### Payoff function
enforcement <- 1

DFall_illegal_1e = data.frame()
Vnext_illegal_1e = vector
V2 = seq(0, 0, length.out = sizex)

actual_optimization <- for(t in T:1)
{
  print(t)
  
  for(i in 1:length(xgrid))
  {
    X = xgrid[i]
    guess = 10
    
    Fishes = optim(par = guess,
                   fn = payoff_illegal,
                   lower = 0,
                   upper = X,
                   X = X,
                   V2 = V2,
                   method = 'L-BFGS-B')
    
    hactual = Fishes$par # Actual harvest
    value = -Fishes$value # Value of the actual harvest
    Vnext[i] = value
    
    ### DF to store information to store information
    DFnow_illegal_1e = data.frame(time = t, X = X, hactual = hactual, value = value)
    DFall_illegal_1e = bind_rows(DFall_illegal_1e, DFnow_illegal_1e)
  }

  V2 = Vnext # tells the model to iterate  

}


#### Forward Simulation

DF_opt_illegal_1e <- DFall_illegal_1e %>% 
  filter(time == 1)

xsim2 = vector()
hsim2 = vector()

xsim2[1] = int_stock
Tsim = seq(1, 20)

for(t in Tsim)
{
  Fishes2 = spline(x = DF_opt_illegal_1e$X, y = DF_opt_illegal_1e$hactual, xout = xsim2[t])
  hsim2[t] = Fishes2$y
  if(t < max(Tsim))
  {
   xsim2[t+1] = stock_growth_fun(h = hsim2[t], X = xsim2[t]) 
  }
}

DFsimulation_1e <- data.frame(time = Tsim, xsim = xsim2, hsim = hsim2) %>%
  mutate(enfE = rep("1", 20)) %>% 
  mutate(stock = round(xsim)) %>% 
  mutate(legal = round(spline(x = DFopt$X, y = DFopt$hstar, xout = xsim)$y)) %>% 
  mutate(legal = ifelse(legal > hsim, round(hsim), legal)) %>% 
  mutate(illegal = round(hsim - legal)) %>% 
  mutate(illegal = ifelse(illegal < 0, 0, illegal)) %>% 
  mutate(total = legal + illegal)
```


### Visuals


#### Policy Function


```{r, warning=FALSE}
policy_harvest_plot <- ggplot(data = DFall) +
  geom_path(aes(x = X, y = hstar, color = factor(time)), size = 1.3) +
  xlab("Stock (MT)") +
  ylab("Harvest (MT)") +
  scale_x_continuous(label=comma) +
  scale_y_continuous(label=comma) +
  scale_color_viridis_d() +
  ggtitle(stringr::str_wrap("Indian Ocean Yellowfin Tuna: Policy Function", width=30)) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

policy_harvest_plot <- policy_harvest_plot +
  theme(legend.position = "none")

policy_harvest_plot_final <- plot_grid(policy_harvest_plot,
                                       ncol = 1,
                                       nrow = 1,
                                       # labels = c("A"),
                                       label_fontfamily = "calibri",
                                       label_fontface = "plain")

policy_harvest_plot_final
```


#### Value Function

```{r}
policy_value_plot <- ggplot(data = DFall) +
  geom_path(aes(x = X, y = Vstar, color = factor(time)), size = 1.3) + #value
  xlab("Stock (MT)") +
  ylab("Value") +
  scale_y_continuous(label=comma) +
  scale_x_continuous(label=comma) +
  scale_color_viridis_d() +
  ggtitle(stringr::str_wrap("Indian Ocean Yellowfin Tuna: Value Function", width=30)) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

policy_value_plot <- policy_value_plot +
  theme(legend.position = "none")

policy_value_plot

policy_value_plot_final <- plot_grid(policy_value_plot,
                                       ncol = 1,
                                       nrow = 1,
                                       # labels = c("B"),
                                       label_fontfamily = "calibri",
                                       label_fontface = "plain")

policy_value_plot_final
```


#### Optimal Stock Growth

```{r}
opt_stock_plot <- ggplot(data = DFsimulation) +
  geom_line(aes(x = time, y = xsim), color = "skyblue", size = 1.7) +
  geom_point(aes(x = time, y = xsim), color = "purple4") +
  xlab("Year") +
  ylab("Stock (MT)") +
  scale_y_continuous(label=comma) +
  ggtitle(stringr::str_wrap("Indian Ocean Yellowfin Tuna: Optimal Stock Growth", width=30)) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

opt_stock_plot

opt_stock_plot_final <- plot_grid(opt_stock_plot,
                                       ncol = 1,
                                       nrow = 1,
                                       labels = c("C"),
                                       label_fontfamily = "calibri",
                                       label_fontface = "plain")

opt_stock_plot_final
```


#### Optimal Harvest Policy

```{r}
opt_harvest_plot <- ggplot(data = DFsimulation) +
  geom_line(aes(x = time, y = hsim), color = "skyblue", size = 1.7) +
  geom_point(aes(x = time, y = hsim), color = "purple4") +
  xlab("Year") +
  ylab("Harvest (MT)") +
  scale_y_continuous(label=comma) +
  ggtitle(stringr::str_wrap("Indian Ocean Yellowfin Tuna: Optimal Harvest", width=30)) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

opt_harvest_plot

opt_harvest_plot_final <- plot_grid(opt_harvest_plot,
          ncol = 1,
          nrow = 1,
          labels = c("D"),
          label_fontfamily = "calibri",
          label_fontface = "plain")

opt_harvest_plot_final
```


#### All Stocks


```{r, warning=FALSE}
DFsimulation_all <- bind_rows(DFsimulation, 
                     DFsimulation_0e, 
                     DFsimulation_0.25e, 
                     DFsimulation_0.5e, 
                     DFsimulation_0.75e, 
                     DFsimulation_1e)


DFsimulation_enf <- DFsimulation_all %>% 
  filter(enfE != "Optimal")

all_stock_plot <- ggplot(data = DFsimulation_enf) +
  geom_line(aes(x = time, y = xsim, color = enfE), size = 1.5) +
  xlab("Year") +
  ylab("Stock (MT)") +
  scale_y_continuous(label = comma) +
  scale_color_viridis_d(direction = -1, option = "D") +
  guides(colour = guide_legend(reverse=T)) +
  labs(color = "Enforcement Level") +
  ggtitle(stringr::str_wrap("Yellowfin Tuna Stocks Under Varying Levels of Enforcement", width = 30)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.title.x = element_text(size = 18),  # X-axis title size
        axis.title.y = element_text(size = 18),  # Y-axis title size
        axis.text.x = element_text(size = 12),   # X-axis labels size
        axis.text.y = element_text(size = 12)) + #,   # Y-axis labels size
  guides(color = FALSE)
        # legend.title = element_text(size = 16),  # Legend title size
        # legend.text = element_text(size = 12))

all_stock_plot

# all_stock_plot_final <- plot_grid(all_stock_plot,
#           ncol = 1,
#           nrow = 1,
#           labels = c("D"),
#           label_fontfamily = "calibri",
#           label_fontface = "plain")
# 
# all_stock_plot_final
```


#### All  Harvests

```{r}
all_stock_plot <- ggplot(data = DFsimulation_enf) +
  geom_line(aes(x = time, y = hsim, color = enfE), size = 1) +
  xlab("Year") +
  ylab("Harvest (MT)") +
  scale_y_continuous(label = comma) +
  scale_color_viridis_d(direction = -1, option = "D") +
  guides(colour = guide_legend(reverse=T)) +
  labs(color = "Enforcement Level") +
  ggtitle(stringr::str_wrap("Yellowfin Tuna Harvest Under Varying Levels of Enforcement", width = 30)) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

all_stock_plot
```

#### Optimal E

```{r}
# harvest_range = c(0, 650000)
# 
# e_opt_plot <- ggplot(data = DFsimulation) +
#   geom_line(aes(x = time, y = xsim), color = "skyblue", size = 1) +
#   geom_line(aes(x = time, y = hsim), color = "deeppink4", size = 1) +
#   xlab("Year") +
#   scale_y_continuous(name = "Stock (MT)", label = comma,
#                      sec.axis = sec_axis(~., name="Harvest (MT)", breaks = harvest_range, label = comma)) +
#   theme(axis.title.y = element_text(color = "skyblue", size=13),
#     axis.title.y.right = element_text(color = "deeppink4", size=13)) +
#   theme_minimal()
# 
# e_opt_plot

sum(DFsimulation$illegal + DFsimulation$legal)

DFsimulation_p <- DFsimulation %>% select(time, illegal, legal) %>% 
  pivot_longer(-time, names_to = "harvest_type", values_to = "harvest")

e_opt_plot <- ggplot(data = DFsimulation_p) +
  geom_col(aes(x = time, y = harvest, fill = harvest_type)) +
  scale_fill_manual(values = c("legal" = "#336e94", "illegal" = "firebrick4"),
                    labels = c("Illegal Harvest", "Legal Harvest")) +
  scale_y_continuous(limits = c(0, 650000), label = comma) +
  labs(x = "Year", y = "Harvest (MT)") +
  ggtitle("Optimal Harvest Intensity \n (Total = 2,145,349 MT)") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  theme(plot.title = element_text(hjust = 0.5))


e_opt_plot

e_opt_plot_final <- plot_grid(e_opt_plot,
          ncol = 1,
          nrow = 1,
          # labels = c("E"),
          label_fontfamily = "calibri",
          label_fontface = "plain")

e_opt_plot_final
```

#### Enforcement = 0

```{r}
sum(DFsimulation_0e$illegal + DFsimulation_0e$legal)

DFsimulation_0e_p <- DFsimulation_0e %>% select(time, illegal, legal) %>% 
  pivot_longer(-time, names_to = "harvest_type", values_to = "harvest")

e_0_plot <- ggplot(data = DFsimulation_0e_p) +
  geom_col(aes(x = time, y = harvest, fill = harvest_type)) +
  scale_fill_manual(values = c("legal" = "#336e94", "illegal" = "firebrick4"),
                    labels = c("Illegal Harvest", "Legal Harvest")) +
  scale_y_continuous(limits = c(0, 650000), label = comma) +
  labs(x = "Year", y = "Harvest (MT)") +
  ggtitle("Harvest Intensity with No Enforcement \n (Total = 1,111,129 MT)") +
theme_classic() +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.title.x = element_text(size = 18),
        axis.title.y = element_text(size = 18),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12)) +
  guides(fill = FALSE)

e_0_plot

e_0_plot_final <- plot_grid(e_0_plot,
          ncol = 1,
          nrow = 1,
          # labels = c("F"),
          label_fontfamily = "calibri",
          label_fontface = "plain")

e_0_plot_final
```



#### Enforcement = 0.25

```{r}
sum(DFsimulation_0.25e$illegal + DFsimulation_0.25e$legal)

DFsimulation_0.25e_p <- DFsimulation_0.25e %>% select(time, illegal, legal) %>% 
  pivot_longer(-time, names_to = "harvest_type", values_to = "harvest")

e_0.25_plot <- ggplot(data = DFsimulation_0.25e_p) +
  geom_col(aes(x = time, y = harvest, fill = harvest_type)) +
  scale_fill_manual(values = c("legal" = "#336e94", "illegal" = "firebrick4"),
                    labels = c("Illegal Harvest", "Legal Harvest")) +
  scale_y_continuous(limits = c(0, 650000), label = comma) +
  labs(x = "Year", y = "Harvest (MT)") +
  ggtitle("Harvest Intensity at 25% Enforcement \n (Total = 1,362,307 MT)") +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.title.x = element_text(size = 18),
        axis.title.y = element_text(size = 18),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12)) +
  guides(fill = FALSE)


e_0.25_plot

e_0.25_plot_final <- plot_grid(e_0.25_plot,
          ncol = 1,
          nrow = 1,
          # labels = c("G"),
          label_fontfamily = "calibri",
          label_fontface = "plain")

e_0.25_plot_final
```

#### Enforcement = 0.5
```{r}
sum(DFsimulation_0.5e$illegal + DFsimulation_0.5e$legal)

DFsimulation_0.5e_p <- DFsimulation_0.5e %>% select(time, illegal, legal) %>% 
  pivot_longer(-time, names_to = "harvest_type", values_to = "harvest")

e_0.5_plot <- ggplot(data = DFsimulation_0.5e_p) +
  geom_col(aes(x = time, y = harvest, fill = harvest_type)) +
  scale_fill_manual(values = c("legal" = "#336e94", "illegal" = "firebrick4"),
                    labels = c("Illegal Harvest", "Legal Harvest")) +
  scale_y_continuous(limits = c(0, 650000), label = comma) +
  labs(x = "Year", y = "Harvest (MT)") +
  ggtitle("Harvest Intensity at 50% Enforcement \n (Total = 1,889,212 MT)") +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.title.x = element_text(size = 18),
        axis.title.y = element_text(size = 18),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12)) +
  guides(fill = FALSE)


e_0.5_plot

e_0.5_plot_final <- plot_grid(e_0.5_plot,
          ncol = 1,
          nrow = 1,
          # labels = c("H"),
          label_fontfamily = "calibri",
          label_fontface = "plain")

e_0.5_plot_final
```


#### Enforcement = 0.75

```{r}
sum(DFsimulation_0.75e$illegal + DFsimulation_0.75e$legal)

DFsimulation_0.75e_p <- DFsimulation_0.75e %>% select(time, illegal, legal) %>% 
  pivot_longer(-time, names_to = "harvest_type", values_to = "harvest")

e_0.75_plot <- ggplot(data = DFsimulation_0.75e_p) +
  geom_col(aes(x = time, y = harvest, fill = harvest_type)) +
  scale_fill_manual(values = c("legal" = "#336e94", "illegal" = "firebrick4"),
                    labels = c("Illegal Harvest", "Legal Harvest")) +
  scale_y_continuous(limits = c(0, 650000), label = comma) +
  labs(x = "Year", y = "Harvest (MT)") +
  ggtitle("Harvest Intensity at 75% Enforcement \n (Total = 2,217,507 MT)") +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.title.x = element_text(size = 18),
        axis.title.y = element_text(size = 18),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12)) +
  guides(fill = FALSE)


e_0.75_plot

e_0.75_plot_final <- plot_grid(e_0.75_plot,
          ncol = 1,
          nrow = 1,
          # labels = c("I"),
          label_fontfamily = "calibri",
          label_fontface = "plain")

e_0.75_plot_final
```


#### Enforcement = 1
```{r}
sum(DFsimulation_1e$illegal + DFsimulation_1e$legal)

DFsimulation_1e_p <- DFsimulation_1e %>% select(time, illegal, legal) %>% 
  pivot_longer(-time, names_to = "harvest_type", values_to = "harvest")

e_1_plot <- ggplot(data = DFsimulation_1e_p) +
  geom_col(aes(x = time, y = harvest, fill = harvest_type)) +
  scale_fill_manual(values = c("legal" = "#336e94", "illegal" = "firebrick4"),
                    labels = c("Illegal Harvest", "Legal Harvest")) +
  scale_y_continuous(limits = c(0, 650000), label = comma) +
  labs(x = "Year", y = "Harvest (MT)") +
  ggtitle("Harvest Intensity with Full Enforcement \n (Total = 2,145,349 MT)") +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.title.x = element_text(size = 18),
        axis.title.y = element_text(size = 18),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12)) +
  guides(fill = FALSE)


e_1_plot

e_1_plot_final <- plot_grid(e_1_plot,
          ncol = 1,
          nrow = 1,
          # labels = c("J"),
          label_fontfamily = "calibri",
          label_fontface = "plain")

e_1_plot_final
```


#### All Enforcement Harvest
```{r}
plot_grid(e_0_plot_final, e_0.25_plot_final, e_0.5_plot_final, e_0.75_plot_final, e_1_plot_final, e_opt_plot_final,
          labels = c("1", "2", "3", "4", "5", "6"),
            ncol = 2)
```


### Summary Table

```{r}
summary_df_2 <- data.frame(
  Enforcement = c(0, 0.25, 0.5, 0.75, 1, "Optimal"),
  Stock_start = c(int_stock, int_stock, int_stock, int_stock, int_stock, int_stock),
  Stock_end = c((1), (3118), (126855), (556055), (914558), (9145697)),
  Illegal = c(sum(DFsimulation_0e$illegal), sum(DFsimulation_0.25e$illegal), sum(DFsimulation_0.5e$illegal), sum(DFsimulation_0.75e$illegal), sum(DFsimulation_1e$illegal), sum(DFsimulation$illegal)),
  Legal = c(sum(DFsimulation_0e$legal), sum(DFsimulation_0.25e$legal), sum(DFsimulation_0.5e$legal), sum(DFsimulation_0.75e$legal), sum(DFsimulation_1e$legal), sum(DFsimulation$legal)),
  Total = c(sum(DFsimulation_0e$total), sum(DFsimulation_0.25e$total), sum(DFsimulation_0.5e$total), sum(DFsimulation_0.75e$total), sum(DFsimulation_1e$total), sum(DFsimulation$total))
)

summary_df_2 <- summary_df_2 %>% 
  arrange(Enforcement) %>% 
  select(-Enforcement, everything()) %>% 
  rename("Enforcement Level" = Enforcement,
         "Starting Biomass (MT)" = Stock_start,
         "Ending Biomass (MT)" = Stock_end,
         "Illegal Harvest" = Illegal,
         "Legal Harvest" = Legal,
         "Total Harvest (MT)" = Total)

summary_df_last <- summary_df_2 %>% 
  mutate(`Illegal Harvest` = paste0(round(`Illegal Harvest`/`Total Harvest (MT)`*100, digits = 2), "%")) %>% 
  mutate(`Legal Harvest` = paste0(round(`Legal Harvest`/`Total Harvest (MT)`*100, digits = 2), "%"))


summary_df_final <- summary_df_last %>%
  kbl(caption = "Stock Dynamics and Harvest Across Different Enforcement Levels") %>%
  kable_classic(full_width = F, html_font = "Calibri", position = "left") %>% 
  column_spec(ncol(summary_df_last), bold = TRUE) %>% 
  row_spec(6, color = "skyblue")
  
  kable(summary_df_2, caption = "Stock Dynamics and Harvest Across Different Enforcement Levels")
```

```{r}
summary_df_final
```
